### 2013-06-18 ms_V3.tex
Biblio_fusion+lines numberingin the review +orthograph corrections

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{color,lineno,setspace,graphicx,multirow,kpfonts}
\usepackage[top=2.4cm,left=2.4cm,top=2.4cm,bottom=2.4cm,includefoot]{geometry}
\usepackage[style=bes]{biblatex}
\bibliography{./library, EKLOF,CHEUNG,THUILLER,CANARD, POISOT, WILLIAMS, HAVENS, BAISER, PEREIRA, WHITEHEAD, STOUFFER, STOU2, ALLESINA, ALLOUCHE, ALBOUY, FROESE, JACKSON,STANKO}
%\bibliograph{library}

@@

Current global changes make it important to be able to predict which
interactions will occur in emerging ecosystems. Most of the current methods to
infer the existence of interactions between two species require a good knowledge
of their behaviour or a direct observation of interactions. In this paper, we
overcome these limitations by developing a method, inspired from the niche model
of food web structure, using the statistical relationship between predator and
prey body size to infer the matrix of potential interactions among a pool of
species. The novelty of our approach is to infer, for any species of a given
species pool, the three species specific parameters of the niche model. The
method applies to both local and metaweb scales. It allows one to evaluate the
feeding interactions of a new species entering the community. We find that this
method gives robust predictions of the structure of food webs, and that its
efficiency is increased when the strength of the body- size relationship between
predators and preys increases. We finally illustrate the potential of the method
to infer the metaweb structure of pelagic fishes of the Meditarrannean sea under
different global change scenarios.

@@

%------------------------------------------------------------
\section{Introduction}
One of the current challenges in ecology is to predict the emergence and
re-assembly of communities following species responses to global changes.
Understanding this is made all the more important as these novel ecosystems will
be more common with increasing human pressure. We know that species invasions,
biomass harvesting, ranges shifts, disturbances and changes in land use are
important drivers of biodiversity turnover. How they affect species composition
is now well described \parencite{Pereira2010}, but forecasting their impact on
community structure and functioning requires \emph{a priori} knowledge of
potential interactions among species. Predicting interactions among species that
never co-occurred proves challenging, as traditional empirical methods of food
web sampling such as stomacal content analysis cannot be applied. While for
competitive communities this task could be achieved using predictive modeling
based on functional traits \parencite{McGill2006, Albouy2010} or phylogeny
\parencite{Cavender-Bares2009, Mouquet2012} , it is much more difficult to
forecast trophic interactions in a food web \parencite{Ings2009,
Tylianakis2008,Montoya2010}.

@@

Development of predictive models of trophic interactions could greatly improve
our understanding of large scale food web structure and our capacity to
anticipate major changes in ecosystem functionning. Theory should provide some
guidance about the general rules underpinning interactions among a set of
species and thus help us to infer the metaweb. The actual food web theory is
largely derived from the niche model \parencite{Williams2000}. This model simply
and intuitively poses that each species in a food web has a niche position
$n_i$, a feeding niche optimum $c_i$ and a range $r_i$ of suitable preys around
that optimum (Fig. 1). These simples rules are sufficient to generate realistic
food web structures that fit most of published food webs \parencite{Dunne2006}.
The niche model was a substantial improvement of the previous cascade model
(Cohen1990) and subsequent models (e.g. the nested hierachy model
\parencite{Cattin2004}, the minimum potential model \parencite{Allesina2008},
the probabilistic niche model \parencite{Williams2010} are somehow derived from
these rules \parencite{Stouffer2005}. Although it is based on different
assumptions, the adaptive foraging theory of food web structure
\parencite{Petchey2008b} provides comparable predictions
\parencite{Williams2010}. One major recent breakthrough in food web theory have
been the attempts to parameterize the niche model and other food web models from
field data and to compare their fit through likelihood methods
\parencite{Allesina2008, Williams2010, Williams2011}. These methods provide, for
each species of the food web, the optimal parameters to fit the empirical web
structures, given the hypothesized underlying rules of the niche model.

@@

In this paper, we present a method designed to infer the potential interactions
between all pairs of species of a species pool based on observations of body
size of predators and their prey. The method applies to both the local and the
metaweb scales. We do so by a parameterization of the niche model, based on the
well-documented allometric scaling relationship between predator and prey
\parencite{Cohen2003, Brose2006, Riede2010}. We first develop the method and
apply it to food webs from various environments. We find the method accurately
predicts the interactions (and lack thereof), and that the accuracy increases
with the strength of the predator-prey body size relationship. We then analyze
the sensitivity of the method to incomplete data (missing links) and find that
it is robust to sampling effort. We finally illustrate the potential of the
method to infer the metaweb structure of pelagic fishes of the Meditarrannean
sea and the consequences of alteration of body size distribution by global
changes or anthropic forcings. The method is best suited for strongly
size-structured food webs and will likely not hold for other types of
non-body-size structured interactions. We therefore conclude on the future
issues to generalize this approach to other types of trait matching models.

@@

The method aims to infer the potential interactions among a pool of species from
a subset of observations of predator-prey interactions. The method follows the
following steps, with details provided below:
\begin{description}
\item[Step 1:] Log transformation of the body size data;
\item[Step 2:] Statistical analysis of the predator-prey body size relationship;
\item[Step 3:] Inferrence of the niche model parameters for all species from the species pool;
\item[Step 4:] Interpretation of the parameters and computation of the metaweb.
\end{description}
We also provide an example of R code (R Core Development Team) and data in the Supplementary Material, detailling the step by step procedure and the format of the input data.

@@

Assuming that body size is the main niche axis structuring trophic interactions,
the parameter $n_i$ corresponds simply to the log of body size (in mass or
length) of species $i$. Though only the relative position of all species along
the body size gradient needs to be respected, it is possible to standardize log
body size values between 0 (minimum size in the regional species pool) and 1
(maximal size). We then consider a linear relationship between the decimal
logarithm of body size and the centroid of the niche (the dark line at Fig. 1).
This relationship is obtained by fitting the linear model $c =
\mathrm{log}_{10}(M_{prey})=\alpha_0 +
\alpha_1\times\mathrm{log}_{10}(M_{pred})$ to the data, where $M_{prey}$ and
$M_{pred}$ are the prey and predator body size respectively. The lower and upper
boundaries of the feeding range are easily obtained by fitting the 5\% and 95\%
quantile regressions between $\mathrm{log}_{10}(M_{prey})$ and
$\mathrm{log}_{10}(M_{pred})$ (the dotted lines at Fig. 1, see the example at
Fig. 2). We note them as $r_{low,i}$ and $r_{high,j}$ respectively, and the
corresponding parameters of the linear quantile regresions are
$\beta_{0,low/high}$ and $\beta_{1,low/high}$. In sum, the parameter $n_i$ for
any species of the metaweb is given by the standardized value of the log body
size $M_i$, $c_i$ is estimated from the linear regression between predator and
prey log body size and $r_i$ from the quantile regressions. Type I regressions
were used because there is no equivalence of type II models for quantile
regressions.

@@

This result shows that our method of parameterization of the niche model is
robust with regard to sampling effort. Note however that a biased sampling with
respect to body size (e.g. sampling of the largest species) might be more likely
to reduce the fit of the predator-prey body size relationship. The aggregation
intro trophic species that do have the same body size and the same diet should
not impact the prediction since it will not affect parameter evaluation. It will
however reduce the fit of the predator-prey body size relationship and therfore
the accuracy of the method if the species do have different body sizes. The same
artifact will be observed if there is strong intraspecific variation in body
size (see the Discussion).

@@

\subsection{Inferring the metaweb for Mediterrannean fishes}
We estimated parameters $n$, $c$ and $r$ for each of the 557 species and
inferred the potential interactions among all of them (the example in the
Supplementariy code is based on this dataset). The metaweb has a total of 126
501 links, for a connectance of 0.41 (Fig. 5A). The metaweb is also highly
nested (specialist species feed on a subset of prey of the most generalist
species. Fig. 5A). We also considered a second niche axis related to species
spatial distribution. Most fish species have restricted geographic range within
the Mediterranean sea because of specific response to temperature and other
environmental variables \parencite{Albouy2012}. We therefore removed from the
metaweb all links between species having no range overlap. Data on the extent of
occurrence of fish species were compiled from a published atlas of fishes of the
northern Atlantic and the Mediterranean \parencite{Whitehead1986}. This atlas is
based on regional data sets and expert knowledge and was edited between 1984 and
1986. It currently provides the only available basin-wide information on the
extent of occurrence of all Mediterranean Sea fish species. The above mentioned
atlas do not account for the bathymetric distribution of Mediterranean fish
species, yet bathymetry is considered as one of the main factors accounting for
marine fish distributions \parencite{Louisy2005}. We therefore refined the
extent of occurrence maps by clipping off areas with depths that fall outside
the minimum or maximum known for the species. Species' bathymetric ranges were
obtained from FishBase \parencite{Froese2010, Louisy2005}. The resulting metaweb
has a total of 95 989 links, for a connectance of $C = 0.31$. Connectance
decreases because links are removed by incomptabilities in bathymetry but the
total number of species stays constant. This metaweb is clearly less interval
(Fig. 5B). Contiguous gaps in the diet are likely to emerge from modularity in
the co-occurrence matrix \parencite{Araujo2011}. Future studies should explore
how co-occurrence is constraining the topological structure of metawebs.

%------------------------------------------------------------
\subsection{Impact of global changes}
Our method to parameterize the niche model has a unique feature relative to the
original niche model \parencite{Williams2000}: the network properties of the
original model, such as the number of links, food chain length and degree
distribution (the number of in and out feeding links per species), are
controlled by the input parameters (species richness and connectance), wherea
all properties of our parameterized niche model are emergent features of the
predator-prey body size relationship and the frequency distribution of body
size. The connectance in the niche model is fixed by the user; in our case it
strongly depends on the scaling of the feeding range with body size and the
frequency of larger body species.

@@

The method should be completed with other sources of informations to better
predict gaps in the interaction matrix. The original niche model was definitely
inspired by the predator-prey body size relationship, but was intented to be
more general and eventually deal with several niche axes
\parencite{Williams2000}. \textcite{Allesina2008} indeed found that adding a
second axis, creating gaps into the first axis interaction matrix, increases the
fit of the model to empirical data. It also makes the network less interval (a
continuous succession of species diets along the niche axis), a structural issue
of the niche model that was reported by \textcite{Cattin2004} and
\textcite{Bersier2006}. There are numerous sources of information that could be
used to improve the model, such as co-occurrence and functional traits.

Our application with the Mediterannean pelagic fish food web provides an example
of how straightforward it is to add additional information so as to improve the
parameterization. A similar approach could also build on the comptability of
other traits such as phenology, location in the water column or hunting modes.
While the approach we describe here is based on very simple statistics, the next
methodological efforts will also have to take into account more various and
heterogeneous sources of data such as phylogeny \parencite{Eklof2012} and expert
knowledge. Bayesian inference appears a good candidate to achieve goal. It
offers the possibility to constrain the prior distribution of the likelihood of
any pairwise interaction, based on trait matching, using alternative source of
data. The method we employed here was based on the match between predator and
prey traits. This method could be generalized by looking at the match between
all potential traits. \textcite{Eklof2013} indeed found that the match between
only three traits is enough to encompass a vast majority of interactions. But
when such data is not always available, then it might be possible to use
phylogeny as a proxy for a high dimensional trait species, provided that traits
are conserved along the phylogeny \parencite{Mouquet2012}. A bayesian addition
to the model would be to weight the likelihood that species $j$ is a predator of
species $i$, considering that the closest relative of this predator is also a
predator of $i$. It could account for part of the unexplained variation we found
in our analysis, for instance by constraining the range of the diet for some
large predators or by creating holes within the feeding range
\parencite{Rall2011}.

@@

\section{Acknowledgements}
We thank I. Gounand for preparing the food web data. We also thank N. Martinez,
U. Brose and two anonymous reviewers for their constructive comments and
stimulating discussion. DG received financial support from NSERC and Canada
Research Chair program. TP is funded by a MELS-FQRNT post-doctoral fellowship.
\newpage

@@

\subsection*{Figure 3} 
Performance of the parameterized niche model to predict
food web structure for the 11 food webs. A) Relationship between the TSS and the
$R^2$ of the predator-prey body size relationship. B) Partitionning of the
different components of the TSS.

@@

\subsection*{Figure 5} 
Illustration of the metaweb of the Mediterannean pelagic
fishes (interactions in black). Panel A) represents the full metaweb and B) the
same metaweb for which links between species not co-occuring together were
removed (their range overlap for less than $0.1\%$ of the Mediterannean sea).

\subsection*{Figure 6} 
Impacts of altering the body size distribution of
Meditarrennean fishes on the degree distribution of the metaweb. The black line
corresponds to the original metaweb degree distribution. For the first scenario,
we simulated a $40\%$ reduction in average body size and recalculated the
metaweb properties, keeping the predator-prey body size relationship constant
(dotted line). For the second scenario we eliminated the top $40\%$ largest
species and recalculated the metaweb properties (dashed line).

>>>>

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{color,lineno,setspace,graphicx,multirow,kpfonts}
\usepackage[top=2.4cm,left=2.4cm,top=2.4cm,bottom=2.4cm,includefoot]{geometry}
\usepackage[style=bes]{biblatex}
\bibliography{./library}

@@

Current global changes make it important to be able to predict which
interactions will occur in emerging ecosystems. Most of the current methods to
infer the existence of interactions between two species require a good knowledge
of their behavior or a direct observation of interactions. In this paper, we
overcome these limitations by developing a method, inspired from the niche model
of food web structure, using the statistical relationship between predator and
prey body size to infer the matrix of potential interactions among a pool of
species. The novelty of our approach is to infer, for any species of a given
species pool, the three species specific parameters of the niche model. The
method applies to both local and metaweb scales. It allows one to evaluate the
feeding interactions of a new species entering the community. We find that this
method gives robust predictions of the structure of food webs, and that its
efficiency is increased when the strength of the body- size relationship between
predators and preys increases. We finally illustrate the potential of the method
to infer the metaweb structure of pelagic fishes of the Mediterranean sea under
different global change scenarios.

@@

%------------------------------------------------------------
\section{Introduction}
One of the current challenges in ecology is to predict the emergence and
re-assembly of communities following species responses to global changes.
Understanding this is made all the more important as these novel ecosystems will
be more common with increasing human pressure. We know that species invasions,
biomass harvesting, ranges shifts, disturbances and changes in land use are
important drivers of biodiversity turnover. How they affect species composition
is now well described \parencite{Pereira2010}, but forecasting their impact on
community structure and functioning requires \emph{a priori} knowledge of
potential interactions among species. Predicting interactions among species that
never co-occurred proves challenging, as traditional empirical methods of food
web sampling such as stomach content analysis cannot be applied. While for
competitive communities this task could be achieved using predictive modeling
based on functional traits \parencite{McGill2006, Albouy2010} or phylogeny
\parencite{Cavender-Bares2009, Mouquet2012} , it is much more difficult to
forecast trophic interactions in a food web \parencite{Ings2009,
Tylianakis2008,Montoya2010}.

@@

Development of predictive models of trophic interactions could greatly improve
our understanding of large scale food web structure and our capacity to
anticipate major changes in ecosystem functioning. Theory should provide some
guidance about the general rules underpinning interactions among a set of
species and thus help us to infer the metaweb. The actual food web theory is
largely derived from the niche model \parencite{Williams2000}. This model simply
and intuitively poses that each species in a food web has a niche position
$n_i$, a feeding niche optimum $c_i$ and a range $r_i$ of suitable preys around
that optimum (Fig. 1). These simples rules are sufficient to generate realistic
food web structures that fit most of published food webs \parencite{Dunne2006}.
The niche model was a substantial improvement of the previous cascade model
(Cohen1990) and subsequent models (e.g. the nested hierachy model
\parencite{Cattin2004}, the minimum potential model \parencite{Allesina2008},
the probabilistic niche model \parencite{Williams2010} are somehow derived from
these rules \parencite{Stouffer2005}. Although it is based on different
assumptions, the adaptive foraging theory of food web structure
\parencite{Petchey2008b} provides comparable predictions
\parencite{Williams2010}. One major recent breakthrough in food web theory have
been the attempts to parameterize the niche model and other food web models from
field data and to compare their fit through likelihood methods
\parencite{Allesina2008, Williams2010, Williams2011}. These methods provide, for
each species of the food web, the optimal parameters to fit the empirical web
structures, given the hypothesized underlying rules of the niche model.

@@

In this paper, we present a method designed to infer the potential interactions
between all pairs of species of a species pool based on observations of body
size of predators and their prey. The method applies to both the local and the
metaweb scales. We do so by a parameterization of the niche model, based on the
well-documented allometric scaling relationship between predator and prey
\parencite{Cohen2003, Brose2006, Riede2010}. We first develop the method and
apply it to food webs from various environments. We find the method accurately
predicts the interactions (and lack thereof), and that the accuracy increases
with the strength of the predator-prey body size relationship. We then analyze
the sensitivity of the method to incomplete data (missing links) and find that
it is robust to sampling effort. We finally illustrate the potential of the
method to infer the metaweb structure of pelagic fishes of the Mediterranean
sea and the consequences of alteration of body size distribution by global
changes or anthropic forcings. The method is best suited for strongly
size-structured food webs and will likely not hold for other types of
non-body-size structured interactions. We therefore conclude on the future
issues to generalize this approach to other types of trait matching models.

@@

The method aims to infer the potential interactions among a pool of species from
a subset of observations of predator-prey interactions. The method follows the
following steps, with details provided below:
\begin{description}
\item[Step 1:] Log transformation of the body size data;
\item[Step 2:] Statistical analysis of the predator-prey body size relationship;
\item[Step 3:] Inference of the niche model parameters for all species from the species pool;
\item[Step 4:] Interpretation of the parameters and computation of the metaweb.
\end{description}
We also provide an example of R code (R Core Development Team) and data in the Supplementary Material, detailing the step by step procedure and the format of the input data.

@@

Assuming that body size is the main niche axis structuring trophic interactions,
the parameter $n_i$ corresponds simply to the log of body size (in mass or
length) of species $i$. Though only the relative position of all species along
the body size gradient needs to be respected, it is possible to standardize log
body size values between 0 (minimum size in the regional species pool) and 1
(maximal size). We then consider a linear relationship between the decimal
logarithm of body size and the centroid of the niche (the dark line at Fig. 1).
This relationship is obtained by fitting the linear model $c =
\mathrm{log}_{10}(M_{prey})=\alpha_0 +
\alpha_1\times\mathrm{log}_{10}(M_{pred})$ to the data, where $M_{prey}$ and
$M_{pred}$ are the prey and predator body size respectively. The lower and upper
boundaries of the feeding range are easily obtained by fitting the 5\% and 95\%
quantile regressions between $\mathrm{log}_{10}(M_{prey})$ and
$\mathrm{log}_{10}(M_{pred})$ (the dotted lines at Fig. 1, see the example at
Fig. 2). We note them as $r_{low,i}$ and $r_{high,j}$ respectively, and the
corresponding parameters of the linear quantile regressions are
$\beta_{0,low/high}$ and $\beta_{1,low/high}$. In sum, the parameter $n_i$ for
any species of the metaweb is given by the standardized value of the log body
size $M_i$, $c_i$ is estimated from the linear regression between predator and
prey log body size and $r_i$ from the quantile regressions. Type I regressions
were used because there is no equivalence of type II models for quantile
regressions.

@@

This result shows that our method of parameterization of the niche model is
robust with regard to sampling effort. Note however that a biased sampling with
respect to body size (e.g. sampling of the largest species) might be more likely
to reduce the fit of the predator-prey body size relationship. The aggregation
intro trophic species that do have the same body size and the same diet should
not impact the prediction since it will not affect parameter evaluation. It will
however reduce the fit of the predator-prey body size relationship and therefore
the accuracy of the method if the species do have different body sizes. The same
artifact will be observed if there is strong intra-specific variation in body
size (see the Discussion).

@@

\subsection{Inferring the metaweb for Mediterranean fishes}
We estimated parameters $n$, $c$ and $r$ for each of the 557 species and
inferred the potential interactions among all of them (the example in the
Supplementary code is based on this dataset). The metaweb has a total of 126
501 links, for a connectance of 0.41 (Fig. 5A). The metaweb is also highly
nested (specialist species feed on a subset of prey of the most generalist
species. Fig. 5A). We also considered a second niche axis related to species
spatial distribution. Most fish species have restricted geographic range within
the Mediterranean sea because of specific response to temperature and other
environmental variables \parencite{Albouy2012}. We therefore removed from the
metaweb all links between species having no range overlap. Data on the extent of
occurrence of fish species were compiled from a published atlas of fishes of the
northern Atlantic and the Mediterranean \parencite{Whitehead1986}. This atlas is
based on regional data sets and expert knowledge and was edited between 1984 and
1986. It currently provides the only available basin-wide information on the
extent of occurrence of all Mediterranean Sea fish species. The above mentioned
atlas do not account for the bathymetric distribution of Mediterranean fish
species, yet bathymetry is considered as one of the main factors accounting for
marine fish distributions \parencite{Louisy2005}. We therefore refined the
extent of occurrence maps by clipping off areas with depths that fall outside
the minimum or maximum known for the species. Species' bathymetric ranges were
obtained from FishBase \parencite{Froese2011, Louisy2005}. The resulting metaweb
has a total of 95 989 links, for a connectance of $C = 0.31$. Connectance
decreases because links are removed by incompatibilities in bathymetry but the
total number of species stays constant. This metaweb is clearly less interval
(Fig. 5B). Contiguous gaps in the diet are likely to emerge from modularity in
the co-occurrence matrix \parencite{Araujo2011}. Future studies should explore
how co-occurrence is constraining the topological structure of metawebs.

%------------------------------------------------------------
\subsection{Impact of global changes}
Our method to parameterize the niche model has a unique feature relative to the
original niche model \parencite{Williams2000}: the network properties of the
original model, such as the number of links, food chain length and degree
distribution (the number of in and out feeding links per species), are
controlled by the input parameters (species richness and connectance), where
all properties of our parameterized niche model are emergent features of the
predator-prey body size relationship and the frequency distribution of body
size. The connectance in the niche model is fixed by the user; in our case it
strongly depends on the scaling of the feeding range with body size and the
frequency of larger body species.

@@

The method should be completed with other sources of informations to better
predict gaps in the interaction matrix. The original niche model was definitely
inspired by the predator-prey body size relationship, but was intended to be
more general and eventually deal with several niche axes
\parencite{Williams2000}. \textcite{Allesina2008} indeed found that adding a
second axis, creating gaps into the first axis interaction matrix, increases the
fit of the model to empirical data. It also makes the network less interval (a
continuous succession of species diets along the niche axis), a structural issue
of the niche model that was reported by \textcite{Cattin2004} and
\textcite{Bersier2006}. There are numerous sources of information that could be
used to improve the model, such as co-occurrence and functional traits.

Our application with the Mediterranean pelagic fish food web provides an example
of how straightforward it is to add additional information so as to improve the
parameterization. A similar approach could also build on the compatibility of
other traits such as phenology, location in the water column or hunting modes.
While the approach we describe here is based on very simple statistics, the next
methodological efforts will also have to take into account more various and
heterogeneous sources of data such as phylogeny \parencite{Eklof2012} and expert
knowledge. Bayesian inference appears a good candidate to achieve goal. It
offers the possibility to constrain the prior distribution of the likelihood of
any pairwise interaction, based on trait matching, using alternative source of
data. The method we employed here was based on the match between predator and
prey traits. This method could be generalized by looking at the match between
all potential traits. \textcite{Eklof2013} indeed found that the match between
only three traits is enough to encompass a vast majority of interactions. But
when such data is not always available, then it might be possible to use
phylogeny as a proxy for a high dimensional trait species, provided that traits
are conserved along the phylogeny \parencite{Mouquet2012}. A bayesian addition
to the model would be to weight the likelihood that species $j$ is a predator of
species $i$, considering that the closest relative of this predator is also a
predator of $i$. It could account for part of the unexplained variation we found
in our analysis, for instance by constraining the range of the diet for some
large predators or by creating holes within the feeding range
\parencite{Rall2011}.

@@

\section{Acknowledgements}
We thank I. Gounand for preparing the food web data. We also thank N. Martinez,
U. Brose and two anonymous reviewers for their constructive comments and
stimulating discussion. DG received financial support from NSERC and Canada
Research Chair program. TP and CA are funded by a MELS-FQRNT post-doctoral fellowship.
\newpage

@@

\subsection*{Figure 3} 
Performance of the parameterized niche model to predict
food web structure for the 11 food webs. A) Relationship between the TSS and the
$R^2$ of the predator-prey body size relationship. B) Partitioning of the
different components of the TSS.

@@

\subsection*{Figure 5} 
Illustration of the metaweb of the Mediterranean pelagic
fishes (interactions in black). Panel A) represents the full metaweb and B) the
same metaweb for which links between species not co-occurring together were
removed (their range overlap for less than $0.1\%$ of the Mediterranean sea).

\subsection*{Figure 6} 
Impacts of altering the body size distribution of
Mediterranean fishes on the degree distribution of the metaweb. The black line
corresponds to the original metaweb degree distribution. For the first scenario,
we simulated a $40\%$ reduction in average body size and recalculated the
metaweb properties, keeping the predator-prey body size relationship constant
(dotted line). For the second scenario we eliminated the top $40\%$ largest
species and recalculated the metaweb properties (dashed line).
